Language-Based Security for Low-Level MPC

### 2024-09-02 ppdp24/slides.tex
checkpoint

  \begin{exampleblock}{2-Party GMW (Contd.)}
    \begin{itemize}
    \item $\ttt{andgmw}(x,y,z)$:
      \begin{itemize}
      \item Picking dummy for $x,y,z$, we can automatically generate a
        pmf under all possible wire inputs.
      \item Pmf can be queried to verify critical properties-- e.g., the
        uniform distribution of output shares under any input conditions. 
      \end{itemize}
      Once properties of gates are verified, we can show that rep.~invariants
      are maintained in any circuit.
    \end{itemize}

@@

>>>>

  \begin{exampleblock}{2-Party GMW (Contd.)}
    \begin{itemize}
    \item $\ttt{andgmw}(x,y,z)$:
      \begin{itemize}
      \item Picking dummy for $x,y,z$, we can automatically generate a
        pmf under all possible wire inputs.
      \item Pmf can be queried to verify critical properties-- e.g., the
        uniform distribution of output shares under any input conditions. 
      \end{itemize}
      Once properties of gates are verified, we can show that rep.~invariants
      are maintained in any circuit.
      \begin{itemize}
      \item Leverage logics for reasoning about probabilistic programming: Probabilistic
        Separation Logic, Lilac.
      \item Manual proofs, but automated tactics and applicability to any circuit.
      \end{itemize}
    \end{itemize}

@@

\section{Conclusion and Future Work}

\begin{frame}{Future Work}

  \begin{itemize}
  \item Generalize verification to arbitrary prime fields.
  \item Automated type system to eliminate manual proof elements.
  \item Support for concurrency.
  \end{itemize}
